Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-03-10 Milestone_1/01-chap1.Rmd
middle effect size example

As shown in Figure \@ref(fig:powerglm), both F-test and Breusch–Pagan test generally possessed greater power than visual test. Since the settings we were using were not ideal scenarios for visual inference, it was not expected that the visual test would be as good as the conventional test. Our goal was to quantify the ability of human reading residual plot, such that the comparison between human and computer vision model can be made.

@@

>>>>

As shown in Figure \@ref(fig:powerglm), both F-test and Breusch–Pagan test generally possessed greater power than visual test. Since the settings we were using were not ideal scenarios for visual inference, it was not expected that the visual test would be as good as the conventional test. Our goal was to quantify the ability of human reading residual plot, such that the comparison between human and computer vision model can be made. It was also found that there was a huge gap between the conventional curves and the visual test curves at the middle of the plot. We further analysed the lineup with the corresponding effect size. Figure \ref{fig:mid-cubic-lineup-example} and \ref{fig:mid-heter-lineup-example} showed that human was indeed hard to identify the pattern at this level of difficulty. However, we as researchers of this project could tell which was the actual data plot by carefully comparing the plots of the lineup since we knew all possible shapes of the residual plot beforehand.

@@

```{r mid-cubic-lineup-example, fig.cap="An example lineup for the cubic model with effect size equal to 0.18. The answer to this linup is seven. It was not suprised participants could not confidently identify the actual data plot given the pattern was very weak. "}
# merged_survey %>%
#   filter(exp == 2 & type == "cubic" & -0.5< log(effect_size) & log(effect_size) < 0.5) %>%
#   head()

VI_MODEL$plot_lineup(mutate(lineup_dat_big[[59]]$data, .fitted = .pred), 
                        remove_axis = TRUE, 
                        remove_grid_line = TRUE,
                        theme = theme_light())
```

```{r mid-heter-lineup-example, fig.cap="An example lineup for the heteroskedasticity model with effect size equal to 17.5. The answer to this linup is two. The butterfly shape could merely being recognised. "}
# merged_survey %>%
#   filter(exp == 2 & type == "heteroskedasticity" & 2< log(effect_size) & log(effect_size) < 3) %>%
#   .$lineup_id %>%
#   factor()

VI_MODEL$plot_lineup(mutate(lineup_dat_big[[136]]$data, .fitted = .pred), 
                        remove_axis = TRUE, 
                        remove_grid_line = TRUE,
                        theme = theme_light())
```

### 2022-03-10 Milestone_1/_book/thesis.tex
middle effect size example

As shown in Figure \ref{fig:powerglm}, both F-test and Breusch--Pagan test generally possessed greater power than visual test. Since the settings we were using were not ideal scenarios for visual inference, it was not expected that the visual test would be as good as the conventional test. Our goal was to quantify the ability of human reading residual plot, such that the comparison between human and computer vision model can be made.

@@

>>>>

As shown in Figure \ref{fig:powerglm}, both F-test and Breusch--Pagan test generally possessed greater power than visual test. Since the settings we were using were not ideal scenarios for visual inference, it was not expected that the visual test would be as good as the conventional test. Our goal was to quantify the ability of human reading residual plot, such that the comparison between human and computer vision model can be made. It was also found that there was a huge gap between the conventional curves and the visual test curves at the middle of the plot. We further analysed the lineup with the corresponding effect size. Figure \ref{fig:mid-cubic-lineup-example} and \ref{fig:mid-heter-lineup-example} showed that human was indeed hard to identify the pattern at this level of difficulty. However, we as researchers of this project could tell which was the actual data plot by carefully comparing the plots of the lineup since we knew all possible shapes of the residual plot beforehand.

@@

\begin{figure}
\centering
\includegraphics{thesis_files/figure-latex/mid-cubic-lineup-example-1.pdf}
\caption{\label{fig:mid-cubic-lineup-example}An example lineup for the cubic model with effect size equal to 0.18. The answer to this linup is seven. It was not suprised participants could not confidently identify the actual data plot given the pattern was very weak.}
\end{figure}

\begin{figure}
\centering
\includegraphics{thesis_files/figure-latex/mid-heter-lineup-example-1.pdf}
\caption{\label{fig:mid-heter-lineup-example}An example lineup for the heteroskedasticity model with effect size equal to 17.5. The answer to this linup is two. The butterfly shape could merely being recognised.}
\end{figure}
